\chapter[Conclusion]{Conclusions and suggestions for future work}

% Papers 1-3
\section[Chemical abundances]{Large-scale environmental influence on the gas-phase chemical abundances in dwarf galaxies}
We find that the large-scale environment influences the chemical evolution of 
dwarf galaxies by estimating the gas-phase oxygen (O/H) and nitrogen (N/H) 
abundances and the N/O ratio of star-forming dwarf galaxies in SDSS DR7 using 
the Direct $T_e$ method and spectroscopic line flux measurements as reprocessed 
in the MPA-JHU catalog \citep[Douglass et al., 2017, in prep]{Douglass17a,
Douglass17b}.  Due to the minimum redshift limit for detecting the [\ion{O}{2}] 
$\lambda$3727 emission line in SDSS DR7 spectra, only 135 star-forming dwarf 
galaxies are available for analysis with the Direct $T_e$ method.  With this 
sample, we see no difference in the metallicity (O/H) between dwarf galaxies in 
voids and denser regions \citep{Douglass17a}.  Upon closer inspection, we find 
minor shifts in the distributions of gas-phase chemical abundances for void 
dwarf galaxies when compared to dwarf galaxies in denser regions: star-forming 
void dwarf galaxies have higher oxygen abundances (O/H), lower nitrogen 
abundances (N/H), and lower N/O ratios \citep{Douglass17b}.

By deriving a relation between the doubly-ionized oxygen and total oxygen 
abundance in star-forming galaxies, we can expand our sample to consist of 1920 
star-forming dwarf galaxies by removing the dependence on the [\ion{O}{2}] 
$\lambda$3727 doublet.  This larger sample exhibits the same shifts in the 
gas-phase chemical abundances as the smaller, 135 star-forming dwarf galaxy 
sample, but with a much higher statistical significance.  We find that 
star-forming void dwarf galaxies have, on average, 7\% higher oxygen abundances, 
10\% lower nitrogen abundances, and 17\% lower N/O ratios than star-forming 
dwarf galaxies in denser regions.  The large-scale ($\sim 10$ \hMpc) environment 
influences the chemical evolution of star-forming dwarf galaxies.

In addition to studying the large-scale environmental influence on the 
distribution of gas-phase chemical abundances in star-forming dwarf galaxies, we 
also investigate if and how the large-scale environment affects relationships 
between the chemical abundances and various other physical properties of the 
galaxies.  We find that the N/O ratio decreases with increasing metallicity 
rather than a constant value for the N/O ratio as a function of O/H as observed 
in other studies.  This is contrary to what we see in the $M_*$-N/O 
relationship, where we find that some of the star-forming dwarf galaxies have a 
constant value of N/O for a range of masses while the remainder exhibit a 
positive relationship between the stellar mass and N/O ratio.  We make note of a 
different critical mass in the $M_*$-N/O relationship in the two environments, 
where the void dwarf galaxies begin to show evidence of secondary nitrogen 
synthesis at a stellar mass $\sim$0.4 dex lower than for the galaxies in denser 
regions.  Most of our star-forming dwarf galaxies follow the established 
mass-metallicity relation \citep[e.g.,][]{Tremonti04}.

No relationship is observed between the metallicity and \ion{H}{1} mass in our 
sample of star-forming dwarf galaxies, but we find that the N/O ratio decreases 
with increasing \ion{H}{1} mass for a given stellar mass.  The star-forming 
dwarf galaxies also exhibit an increase in the metallicity and N/O ratio with 
increasing color (both $u-r$ and $g-r$).  We see very little correlation with 
SFR for either metallicity or the N/O ratio in dwarf galaxies, but the 
metallicity and N/O ratio decrease with increasing sSFR.  Beyond the large-scale 
environmental influence on the distributions of the gas-phase chemical 
abundances and the critical mass in the $M_*$-N/O relationship, we do not 
observe any significant differences between the star-forming void and wall dwarf 
galaxies in any of these relationships.

We surmise that the differences in the distributions of metallicity and the N/O 
ratio seen in the sample of star-forming dwarf galaxies are due to a large-scale 
environmental influence on their star formation history and evolution.  The 
shift in the gas-phase oxygen abundance distribution could be observational 
evidence for delayed star formation in void galaxies when compared to those in 
denser regions.  This would result in a smaller ratio of stellar mass to dark 
matter halo mass in void galaxies than in dwarf galaxies in denser regions, as 
predicted in simulations by \cite{Jung14} and \cite{Tonnesen15}.  If the void 
galaxies are retaining more oxygen as a result of their deeper potential wells, 
then they would be able to commence secondary nitrogen synthesis earlier, as 
seen in the $M_*$-N/O relation in Fig. \ref{fig:M_NO}.  In addition, the shift 
towards lower N/O ratios in the star-forming dwarf galaxies might be evidence 
that cosmological downsizing is environmentally dependent as predicted by 
\cite{Cen11}.  Our results provide evidence for delayed, ongoing star formation 
in void dwarf galaxies whose dark matter halos ceased coalescing earlier than 
for dwarf galaxies in denser regions.

It has been hypothesized that a special population of extremely metal-poor 
galaxies exist in void regions.  We find no evidence for a special population of 
extremely metal-poor star-forming dwarf galaxies in the voids, as we note an 
equal fraction of low metallicity dwarf galaxies in both the void and denser 
regions.  Due to their low gas-phase oxygen abundances, these 287 dwarf galaxies 
have some of the larger N/O ratios of the star-forming dwarf galaxies sample 
studied.  While the metallicities of these galaxies cause them to stand out in 
the relationships between metallicity and other physical quantities (stellar 
mass, color, (s)SFR), they are not unusual when studying the relationships 
between the N/O ratio and these other quantities.

% Small-scale environment
\section[Small-scale environment]{Small-scale environmental influence on dwarf galaxy evolution}
In addition to the influence of the large-scale environment on the evolution of 
dwarf galaxies, we also study the effects of the small-scale environment on dwarf 
galaxies.  We find that only the presence of a neighboring galaxy within 0.05 
\hMpc or 0.05$r_{vir}$, or the presence of a group within 0.1 \hMpc influences a 
dwarf galaxy's evolution.  Dwarf galaxies with a nearest neighbor galaxy within 
0.05 \hMpc or 0.05$r_{vir}$ are bluer, have a higher sSFR, and have higher 
oxygen and nitrogen abundances than average.  This matches the results of 
\cite{Park09}, who find that late-late type galaxy pairs within 0.05$r_{vir}$ 
are bluer and have higher SFRs.  In contrast, dwarf galaxies within 0.1 \hMpc of 
the center of the closest group are redder, have lower oxygen abundances, and 
have higher N/O ratios than average.  These results are independent of both the 
maximum relative velocity required to define a nearest neighbor and the sample 
(star-forming versus all dwarf galaxies).

When we incorporate the redshift into the distance calculations, we find that 
the galaxies within 0.05$r_{vir}$ are most likely strongly interacting or 
merging with their nearest neighbor.  These merging galaxies likely share the 
same dark matter halo, suggesting that the dark matter halo is more influential 
on a galaxy's evolution than the distance between a galaxy and its nearest 
neighbor.

% GV galaxies
\section[GV galaxies]{Properties of green valley galaxies}
Finally, we also investigate the properties of galaxies residing in the green 
valley of the color-magnitude diagram (CMD) in an effort to understand the role 
of the environment on a galaxy's evolution through the color-magnitude diagram.  
We discover that we can define galaxies which are transitioning through the 
green valley of the CMD by combining the galaxy's color, color gradient, and 
inverse concentration index.  Galaxies with a value less than 25 for the 
morphological type as calculated in the KIAS-VAGC exist in the green valley 
portion of the UV-optical CMD.  Galaxies defined as early types (morphological 
type values equal to 1 or 2) are in the red cloud, while those with 
morphological type values greater than 25 are in the blue sequence.  With this 
quantitative definition for galaxies transitioning through the green valley, we 
can begin to understand the properties of green valley galaxies and their 
evolution.

Based on our analysis, green valley galaxies have stellar masses comparable to 
galaxies in the red cloud.  They have intermediate SFRs and low-to-intermediate 
sSFRs.  Green valley galaxies also have high gas-phase nitrogen abundances 
(N/H), resulting in high N/O ratios.  While their SFRs show that their star 
formation has been quenched, their stellar masses inform us that this is not due 
to any premature quenching mechanism.  The high nitrogen abundances in the green 
valley galaxies indicate that the galaxies are either no longer forming stars 
(since nitrogen is produced in lower mass stars than oxygen), or that the 
galaxies were able to synthesize both primary and secondary nitrogen (heavy 
elements were present during the last few star formation episodes to permit the 
CNO cycle to commence earlier).  This chemical abundance pattern of normal 
oxygen (O/H), high nitrogen (N/H), and high N/O ratio is also seen in galaxies 
classified as AGN, indicating that galaxies in the green valley have an AGN.

There is a higher fraction of faint galaxies from denser regions than faint void 
galaxies in the green valley.  Combined with the previous results about the 
large-scale environmental influence on the gas-phase chemical abundances, this 
indicates that void dwarf galaxies are less evolved than dwarf galaxies in 
denser environments.


\section[Future work]{Suggestions for future work}

% Metallicity
%  - gradients
%  - chemical abundances of composite, AGN galaxies
%  - SHELS?

% GV galaxies
%  - understand aimc calculation
%  - metallicity gradients
%  - small-scale environment

A critical problem in galaxy formation is understanding how galaxies transition 
from the blue sequence to the red cloud in the optical color-magnitude diagram.  
Star formation is thought to be quenching in galaxies moving through the green 
valley, but the relevant baryonic processes (gas cooling, feedback, etc.) are 
very complex and heavily independent.  The enrichment of the interstellar medium 
(ISM) and circumgalactic medium (CGM) of a galaxy involves many complicated 
processes, the interplay of which is not yet well understood.  Investigating the 
star formation history and chemical evolution of galaxies in the green valley 
should provide clues of the movement of a galaxy through the color-magnitude 
diagram.

With the advent of 2-dimensional spectroscopic data from SDSS MaNGA \citep{MaNGA,
SDSS13}, it is possible to examine how the ISM and CGM are enriched over time.  
MaNGA is the first large-scale survey using integral-field spectroscopy, which 
would permit the study of spatially-resolved physical properties of galaxies 
across many different environments, morphologies, and stages of evolution.  In 
particular, it would be instructive to study the gradients of the gas-phase 
chemical abundances of galaxies in order to better understand their evolution 
through the CMD and also the influence of the environment in both large and 
small scales on the chemical evolution of these galaxies.

A better knowledge of the chemical abundances of galaxies with an AGN is also 
crucial to understanding the evolution of galaxies.  Understanding how the 
presence of an AGN affects a galaxy's evolution is currently limited --- at the 
moment, most research is concentrated on the physics within an AGN.  Many 
simulations have been done to test different theories about the role of an AGN 
in a galaxy, and observations are now needed to test the results of the 
simulations.

% Small-scale environment
%  - relative parameter values as a function of distance
%  - visual inspection of mergers

The work done here on the small-scale environment is only the beginning of what 
can be done in this subject area.  In addition to studying the relationship 
between a galaxy's physical parameters and its distance to the nearest neighbor, 
it is also important to look at the ratio of the galaxy's parameters to its 
neighbor's and the distance to the nearest neighbor --- ``galactic 
conformity.''  These comparisons should include a morphological comparison, 
similar to the analysis done by \cite{Park09}.  We also find evidence of 
possible mergers when studying the influence of the small-scale environment.  
Visual inspection of these dwarf galaxies is imperative to confirming this 
conclusion.